The Effect of Oil Price on Field Production: Evidence from the Norwegian Continental Shelf

### 2015-04-02 oil_prices_rr.tex
updated analysis

Estimating a smoothed function of two variables requires a somewhat more involved method.  In particular I use Thin-plate regression spline \citep{wood_thin_2003}. Consider equation \ref{thin_plate_1}.

@@

In the formulation with a two-dimensional smoothed function, it is not possible to estimate a random effects component for computational reasons.

@@

(Intercept)                                  & $-28746.236^{***}$ & $-70463.727^{***}$ & $-58741.031^{***}$ \\
                                             & $(3386.956)$       & $(2942.538)$       & $(2959.556)$       \\
I(in\_place\_oil\_mill\_sm3/100)             & $0.333^{***}$      & $-0.028$           &                    \\
                                             & $(0.009)$          & $(0.023)$          &                    \\
I(cost\_index/10)                            & $-0.005$           & $-0.019^{***}$     & $-0.000$           \\
                                             & $(0.006)$          & $(0.006)$          & $(0.004)$          \\
year                                         & $28.793^{***}$     & $70.938^{***}$     & $58.352^{***}$     \\
                                             & $(3.393)$          & $(2.951)$          & $(2.955)$          \\
I(year^2)                                    & $-0.007^{***}$     & $-0.018^{***}$     & $-0.015^{***}$     \\
                                             & $(0.001)$          & $(0.001)$          & $(0.001)$          \\
I(price/10)                                  & $0.030$            & $0.026$            & $0.008$            \\
                                             & $(0.015)$          & $(0.015)$          & $(0.010)$          \\
I(price\_l1/10)                              & $0.050^{**}$       & $0.034^{*}$        & $0.020$            \\
                                             & $(0.016)$          & $(0.015)$          & $(0.010)$          \\
I(price\_l2/10)                              & $0.070^{***}$      & $0.058^{***}$      & $0.055^{***}$      \\
                                             & $(0.017)$          & $(0.015)$          & $(0.010)$          \\
I(price\_l3)                                 & $0.004^{*}$        &                    &                    \\
                                             & $(0.002)$          &                    &                    \\
I(price\_l4)                                 & $0.003$            &                    &                    \\
                                             & $(0.002)$          &                    &                    \\
I(price\_l5/10)                              & $-0.008$           & $0.010$            & $-0.003$           \\
                                             & $(0.013)$          & $(0.012)$          & $(0.008)$          \\
I(price\_l6/10)                              & $-0.001$           & $0.007$            & $-0.003$           \\
                                             & $(0.012)$          & $(0.011)$          & $(0.008)$          \\
I(price\_l7/10)                              & $0.009$            & $0.008$            & $0.002$            \\
                                             & $(0.012)$          & $(0.011)$          & $(0.008)$          \\
I(price\_l8/10)                              & $-0.004$           & $-0.001$           & $-0.021^{***}$     \\
                                             & $(0.010)$          & $(0.009)$          & $(0.006)$          \\
EDF: s(prod\_year)                           & $6.505^{***}$      &                    &                    \\
                                             & $(7.326)$          &                    &                    \\
I(price\_l3/10)                              &                    & $0.024$            & $0.031^{**}$       \\
                                             &                    & $(0.015)$          & $(0.010)$          \\
I(price\_l4/10)                              &                    & $0.046^{***}$      & $0.026^{**}$       \\
                                             &                    & $(0.013)$          & $(0.009)$          \\
EDF: s(prod\_year,name)                      &                    & $33.287^{***}$     &                    \\

@@

EDF: s(prod\_year,in\_place\_oil\_mill\_sm3) &                    &                    & $28.195^{***}$     \\
                                             &                    &                    & $(28.469)$         \\

@@

Deviance                                     & 2391636.349        & 1980765.291        & 914018.219         \\
Deviance explained                           & 0.843              & 0.870              & 0.940              \\
Dispersion                                   & 1850.403           & 1564.940           & 718.678            \\
R$^2$                                        & 0.835              & 0.865              & 0.937              \\
GCV score                                    & 1879.759           & 1623.406           & 741.957            \\

@@

Num. smooth terms                            & 1                  & 1                  & 1                  \\

>>>>

Estimating a smoothed function of two variables requires a somewhat more involved method.  In particular, a Thin-plate regression spline \citep{wood_thin_2003} is used. Consider equation \ref{thin_plate_1}.

@@

Unfortunately, In the formulation with a two-dimensional smoothed function, it is not possible to estimate a random effects component for computational reasons.

@@

(Intercept)                                  & $0.335^{*}$    & $-4.017^{***}$ & $-574.287^{***}$ \\
                                             & $(0.146)$      & $(0.183)$      & $(51.125)$       \\
I(in\_place\_oil\_mill\_sm3/100)             & $0.337^{***}$  & $-0.014$       &                  \\
                                             & $(0.005)$      & $(0.014)$      &                  \\
I(cost\_index/10)                            & $-0.018^{***}$ & $-0.030^{***}$ & $-0.014^{***}$   \\
                                             & $(0.003)$      & $(0.003)$      & $(0.002)$        \\
I(price/10)                                  & $-0.006$       & $0.014$        & $0.007$          \\
                                             & $(0.009)$      & $(0.010)$      & $(0.006)$        \\
I(price\_l1/10)                              & $0.004$        & $0.021^{*}$    & $0.015^{*}$      \\
                                             & $(0.010)$      & $(0.010)$      & $(0.006)$        \\
I(price\_l2/10)                              & $0.037^{***}$  & $0.047^{***}$  & $0.048^{***}$    \\
                                             & $(0.009)$      & $(0.010)$      & $(0.006)$        \\
I(price\_l3/10)                              & $0.030^{***}$  & $0.025^{**}$   & $0.033^{***}$    \\
                                             & $(0.009)$      & $(0.009)$      & $(0.006)$        \\
I(price\_l4/10)                              & $0.003$        & $0.043^{***}$  & $0.028^{***}$    \\
                                             & $(0.008)$      & $(0.008)$      & $(0.005)$        \\
I(price\_l5/10)                              & $-0.020^{**}$  & $0.012$        & $-0.001$         \\
                                             & $(0.007)$      & $(0.007)$      & $(0.005)$        \\
I(price\_l6/10)                              & $-0.010$       & $0.008$        & $-0.001$         \\
                                             & $(0.007)$      & $(0.007)$      & $(0.004)$        \\
I(price\_l7/10)                              & $-0.008$       & $0.007$        & $0.004$          \\
                                             & $(0.007)$      & $(0.007)$      & $(0.004)$        \\
I(price\_l8/10)                              & $-0.044^{***}$ & $-0.011$       & $-0.027^{***}$   \\
                                             & $(0.006)$      & $(0.007)$      & $(0.004)$        \\
EDF: s(prod\_year)                           & $6.381^{***}$  &                &                  \\
                                             & $(7.249)$      &                &                  \\
EDF: s(year)                                 & $2.768^{***}$  & $3.000^{***}$  & $3.000^{***}$    \\
                                             & $(2.956)$      & $(3.000)$      & $(3.000)$        \\
EDF: s(prod\_year,name)                      &                & $33.002^{***}$ &                  \\

@@

EDF: s(prod\_year,in\_place\_oil\_mill\_sm3) &                &                & $27.445^{***}$   \\
                                             &                &                & $(27.895)$       \\

@@

Deviance                                     & 23062.678      & 19765.833      & 9057.204         \\
Deviance explained                           & 0.848          & 0.870          & 0.940            \\
Dispersion                                   & 5.410          & 5.965          & 2.325            \\
R$^2$                                        & 0.841          & 0.865          & 0.938            \\
GCV score                                    & 18.145         & 16.218         & 7.355            \\

@@

Num. smooth terms                            & 2              & 2              & 2                \\
